\documentclass[pdftex,english,11pt,parskip=half]{scrartcl}
\usepackage{palatino}
\usepackage{mathpazo}
\usepackage[margin=0.55in]{geometry}
%\usepackage{parskip}
\usepackage[compact]{titlesec}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{babel}
\usepackage{framed}
\usepackage{wrapfig}
\usepackage{subfig}
\usepackage[labelfont=bf,font=small,format=plain]{caption}
\usepackage{doi}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage{array}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{float}
%\usepackage[authoryear]{natbib}
\usepackage[numbers]{natbib}
\usepackage{url,hyperref,color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.75}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\newcommand{\fixme}[1]{{\color{red} #1}}
\renewcommand\thesection{\Alph{section}}
\renewcommand{\familydefault}{\sfdefault}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\begin{document}
\addtokomafont{section}{\large}
\def\bf{\normalfont\bfseries}
\pagestyle{empty}

To whom it may concern:

\vspace{0.2in}

Please accept the attached grant proposal ``Improving reproducibility of recording and pre-processing experimental biomedical data" from Principal Investigator Dr. Brooke Anderson and Co-Investigators Dr. Michael Lyons, Mercedes Gonzalez-Juarrero, Marcela Henao-Tamayo, and Gregory Robertson. This proposal is in response  to \textit{RFA-GM-18-002: Training Modules to Enhance the Rigor and Reproducibility of Biomedical Research}.

\vspace{0.1in}

This submission is from Colorado State University and combines researchers who are expert in the use of open source tools for improving computational reproducibility (Anderson and Lyons) and laboratory-based microbiology and immunology researchers focusing on tuberculosis (Gonzalez-Juarrero, Henao-Tamayo, and Robertson). As the proposal includes plans to provide training materials that include training on R programming tools, expertise in R programming would be helpful in evaluating the Proposed Research Education Program.

\vspace{0.1in}

This proposal has not been previously sumbitted in response to a Program Announcement or Request For Applications. The proposal does not include Vertebrate Animals, Biohazards, or Select Agents. The proposal includes Human Subjects Research that is exempt under Exception 1 (Section 46.101 of 45 CFR 46).

\vspace{0.1in}

\noindent \textbf{Please assign the application to the following:}
\begin{description}
 \item \textbf{National Institute of General Medical Sciences (NIGMS).} 
 \end{description}

\vspace{0.1in}

We thank you for the opportunity to submit this proposal. 

\vspace{0.2in}

Regards, 

Brooke Anderson (PI) \\
Michael Lyons (Co-I) \\
Mercedes Gonzalez-Juarrero (Co-I) \\
Marcela Henao-Tamayo (Co-I) \\
Gregory Robertson (Co-I)

1681 Campus Delivery \\
Fort Collins, Colorado 80523-1681 \\
Telephone: 203-508-2738 \\
Email: brooke.anderson@colostate.edu \\


\end{document}
