\documentclass[pdftex,english,11pt,parskip=half]{scrartcl}
\usepackage{palatino}
\usepackage{mathpazo}
\usepackage[margin=0.7in]{geometry}
%\usepackage{parskip}
\usepackage[compact]{titlesec}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{babel}
\usepackage{framed}
\usepackage{wrapfig}
\usepackage{subfig}
\usepackage[labelfont=bf,font=small,format=plain]{caption}
\usepackage{doi}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage{array}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{float}
%\usepackage[authoryear]{natbib}
\usepackage[numbers]{natbib}
\usepackage{url,hyperref,color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.75}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\newcommand{\fixme}[1]{{\color{red} #1}}
\renewcommand\thesection{\Alph{section}}
\renewcommand{\familydefault}{\sfdefault}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\begin{document}
\addtokomafont{section}{\large}
\def\bf{\normalfont\bfseries}
\pagestyle{empty}

\textbf{OVERALL IMPACT:} Reviewers should provide their assessment of the likelihood for the project to strongly advance research education by fulfilling the goal of this R25 Education Program, in consideration of the following review criteria and additional review criteria, as applicable for the project proposed.

\textbf{1. Significance:}

\begin{itemize}
\item Does the proposed program address a key audience and an important aspect or important need in training in rigor and reproducibility?
\item Is there convincing evidence in the application that the proposed program will significantly advance the stated goal of the program?
\end{itemize}

\textbf{2. Investigator(s):}

\begin{itemize}
\item Is the PD/PI capable of providing both administrative and scientific leadership to the development and implementation of the proposed program?
\item Is there evidence that an appropriate level of effort will be devoted by the program leadership to ensure the program's intended goal is accomplished?
\item If the project is collaborative or multi-PD/PI, do the investigators have complementary and integrated expertise; are their leadership approach, governance and organizational structure appropriate for the project?
\end{itemize}

\textbf{3. Innovation:}

\begin{itemize}
\item Taking into consideration the nature of the proposed research education program, does the applicant make a strong case for this program effectively reaching an audience in need of the program's offerings?
\item Where appropriate, is the proposed program develping or utilizing innovative approaches and latest best practices to improve the knowledge and/or skills of the intended audience?
\end{itemize}

\textbf{4. Approach:}

\begin{itemize}
\item Does the proposed program clearly state its goals and objectives, including the audience to be reached, the content to be conveyed, and the intended outcome?
\item Is there evidence that the program is based on a sound rationale, as well as sound educational concepts and principals?
\item Is the plan for evaluation sound and likely to provide information on the effectiveness of the program?
\end{itemize}

\textbf{5. Environment:}

\begin{itemize}
\item Will the scientific and educational environment of the proposed program contribute to its intended goals?
\item Is there a plan to take advantage of this environment to enhance the educational value of the program?
\item Is there tangible evidence of institutional commitment?
\item Where appropriate, is there evidence of collaboration and buy-in among participating programs, departments, and institutions?
\end{itemize}

\textbf{6. Protections for Human Subjects:}

For research that involves human subjects and meets the criteria for one or more of the six categories of research that are exempt from 45 CRF Part 46, evaluate:

\begin{enumerate}
\item the justification for the exemption,
\item human subjects involvement and characteristics, and
\item sources of materials
\end{enumerate}

\textbf{7. Resource Sharing Plan:}

If support for the development, maintenance, or enhancement of software is requested in the application, comment on the proposed software dissemination plan.

\textbf{8. Budget and Period of Support:}

Consider whether the budget and the requested period of support are fully justified and reasonable in relation to the proposed research.


\end{document}