\documentclass[pdftex,english,11pt,parskip=half]{scrartcl}
\usepackage{palatino}
\usepackage{mathpazo}
\usepackage[margin=0.7in]{geometry}
%\usepackage{parskip}
\usepackage[compact]{titlesec}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{babel}
\usepackage{framed}
\usepackage{wrapfig}
\usepackage{subfig}
\usepackage[labelfont=bf,font=small,format=plain]{caption}
\usepackage{doi}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage{array}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{float}
%\usepackage[authoryear]{natbib}
\usepackage[numbers]{natbib}
\usepackage{url,hyperref,color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.75}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\newcommand{\fixme}[1]{{\color{red} #1}}
\renewcommand\thesection{\Alph{section}}
\renewcommand{\familydefault}{\sfdefault}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\begin{document}
\addtokomafont{section}{\large}
\def\bf{\normalfont\bfseries}
\pagestyle{empty}

{\large \textbf{Environment}}

\begin{quotation}
``Will the scientific and educational environment of the proposed program contribute to its intended goals? Is there a plan to take advantage of this environment to enhance the educational value of the program? Is there tangible evidence of institutional commitment? Where appropriate, is there evidence of collaboration and buy-in among participating programs, departments, and institutions?"
\end{quotation}

\begin{itemize}
\item Computers. Access to needed software. Computer services (IT).
\item Library. Access to many recent books online.
\item Teaching expertise?
\item Research Rigor \& Ethics center / training?
\item Tech Transfer
\item Participating departments (and their commitment)
\end{itemize}

\textbf{Video Studio and Editing Bays.} CSU's Morgan Library has a video studio and editing bays that can be used by anyone affiliated with CSU to record and edit video content (\url{https://lib.colostate.edu/technology/video-studio-editing-bays/}). These can be reserved and used for free for up to three hours at a time. This facility includes microphones, video lights, video recording equipment, and video editing software.

\textbf{Computer Assisted Teaching Support (CATS) Laboratory.} Staff and facilities for professional video recording and editing. \textit{If we need a cost share for this proposal, their contribution could potentially be in-kind.}

\end{document}